Predicting computational reproducibility of data analysis pipelines \\in large population studies using collaborative filtering

### 2018-08-17 paper.tex
Release 0.1!
Added Ali as co-author as he helped produce the data

\author{Soudabeh Barghi, Lalet Scaria, Tristan Glatard\\
  Department of Computer Science and Software Engineering\\ Concordia University, Montreal, Quebec, Canada\\
  {first.last}@concordia.ca \vspace*{-0.5cm}}

@@

\section{Results}
\label{sec:results}
We conducted two experiments for each reproducibility matrix, to evaluate the performance of our 
predictions using (1) ALS without biases, and (2) ALS with subject and file biases. We 
compare the performance of our sampling methods to (1) a dummy 
classifier that always predicts the value in the majority class and (2) 
the Random Unreal method, used as the baseline sampling technique. All 
reported values are averages over 5 repetitions. Due to sampling 
issues, it is possible that the actual training ratio obtained with 
some of the sampling methods does not exactly
match the target one. We checked that the difference between the target 
and real training ratios was lower than 0.01. We used Spark's ALS model 
as available in \texttt{pyspark.ml}, with 50 factors, a 
regularization parameter of 0.01, a maximum of 5 iterations and non 
negative constraints set to true. The code and data used to obtain the results are available through GitHub at
\url{https://github.com/big-data-lab-team/paper-reproducibility-collaborative-filtering}.
\todo{Soudabeh: push your code to reprotools. Tristan: release and check.}
\todo{publish code on zenodo}

%~ , sensitivity and specificity defined as follows:
%~ \[
        %~ Accuracy = \frac{TP+TN}{TP+TN+FP+FN}
%~ \]
%~ \[
        %~ Sensitivity = \frac{TP}{TP+FN}
%~ \]
%~ \[
        %~ Specificity = \frac{TN}{TN+FP}
%~ \]
%~ Where TP is the number of True Positives (correctly predicted reproducibility errors), 
%~ FP is the number of False Positives, TN is the number of true negatives 
%~ and FN is the number of false negatives. \todo{Check if we want to report sensitivity and specificity, otherwise remove.}

@@

@@

\begin{figure}
\centering
\includegraphics[width=0.6\columnwidth]{figures/RFNU_FS100F_ALS_06_test_data_matrix_run1.png}
\caption{Prediction results for RFNU on the Freesurfer dataset, $\alpha=0.6$.}
\label{fig:error-locality}
\end{figure}

>>>>

\author{Soudabeh Barghi, Lalet Scaria, Ali Salari, Tristan Glatard\\
  Department of Computer Science and Software Engineering\\ Concordia University, Montreal, Quebec, Canada}

@@

\section{Results}
\label{sec:results}
We conducted two experiments for each reproducibility matrix, to evaluate the performance of our 
predictions using (1) ALS without biases, and (2) ALS with subject and file biases. We 
compare the performance of our sampling methods to (1) a dummy 
classifier that always predicts the value in the majority class and (2) 
the Random Unreal method, used as the baseline sampling technique. All 
reported values are averages over 5 repetitions. Due to sampling 
issues, it is possible that the actual training ratio obtained with 
some of the sampling methods does not exactly
match the target one. We checked that the difference between the target 
and real training ratios was lower than 0.01. We used Spark's ALS model 
as available in \texttt{pyspark.ml}, with 50 factors, a 
regularization parameter of 0.01, a maximum of 5 iterations and non 
negative constraints set to true. The code and data used to obtain the results are available through GitHub at
\url{https://github.com/big-data-lab-team/paper-reproducibility-collaborative-filtering}.

%~ , sensitivity and specificity defined as follows:
%~ \[
        %~ Accuracy = \frac{TP+TN}{TP+TN+FP+FN}
%~ \]
%~ \[
        %~ Sensitivity = \frac{TP}{TP+FN}
%~ \]
%~ \[
        %~ Specificity = \frac{TN}{TN+FP}
%~ \]
%~ Where TP is the number of True Positives (correctly predicted reproducibility errors), 
%~ FP is the number of False Positives, TN is the number of true negatives 
%~ and FN is the number of false negatives.

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.6\columnwidth]{figures/RFNU_FS100F_ALS_06_test_data_matrix_run1.png}
\caption{Prediction results for RFNU on the Freesurfer dataset, $\alpha=0.6$.}
\label{fig:error-locality}
\end{figure}

@@
